Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-10-01 paper.tex
rewording conclusion a bit

Different modeling choices can have a significant impact on the outcome of a
simulation.  With discrete reactor modeling many factors must be considered in
order to ensure the integrity of conclusions.  Individual reactor outage
modeling can be very useful for certain analyses, but it can reduce result
quality if things such as cycle staggering are not handled appropriately.  The
fleet and discreet modeling done here is itself multi-dimensional. If fuel
sharing is of interest, but cycle staggering is not, individual reactors can
be used with the power capacity lowered and the outage reduced to zero
duration making the capacity factor included in the reactor's power capacity.
Modeling reactors individually can provide valuable insight not possible with
the fleet-based reactor modeling.  For example, bringing reactors back online
following shortage-induced outages should not follow the natural pacing of
fuel availability, otherwise refueling cycles become unsatisfactorily
synchronized.

Increasing the time steps increases facilities' standing inventory requirement
for avoiding supply constraints.  Facilities can provide no more inventory
than they can hold on a single time step.  So increasing time step duration
for a facility with unconstrained supply generally means higher standing
inventories are required in order to achieve equal throughput. Facilities that
have unconstrained supply and very large inventory buffers, are not affected
meaningfully by the time step. Even when facilities do not have individual
inventory or throughput limits, the time step can still have a significant
effect. In recycle loops there is a constraint on how fast material is
introduced through the loop (i.e. the discharge rate of spent fuel from
reactors).  The \emph{inventory drawdown effect} can impact the aggregate
throughput of the recycling loop.

@@

>>>>

Different modeling choices can have a significant impact on the outcome of a
simulation.  With discrete reactor modeling many factors must be considered in
order to ensure the integrity of conclusions.  Individual reactor outage
modeling can be very useful for certain analyses, but it can reduce result
quality if things such as cycle staggering are not handled appropriately.  The
fleet and discreet models used here are just two points in a multi-dimensional
spectrum of modeling choices. If fuel sharing is of interest, but cycle
staggering is not, individual reactors can be used with the power capacity
lowered and the outage reduced to zero duration making the capacity factor
included in the reactor's power capacity.

Modeling reactors individually can provide valuable insight not possible with
the fleet-based reactor modeling.  For example, bringing reactors back online
following shortage-induced outages should not necessarily follow the natural
pacing of fuel availability, otherwise refueling cycles become
unsatisfactorily synchronized.  If individual reactor modeling fidelity is not
required, then performance benefits in both simulation run time and data
analysis may suggest a fleet-based modeling approach.

Increasing time step duration increases facilities' standing inventory
requirement during supply constrained periods.  Facilities can provide no more
inventory than they can hold on a single time step.  So increasing time step
duration for a facility with unconstrained supply generally means higher
standing inventories are required in order to achieve equal throughput.
Facilities with large inventory buffer that are unconstrained are not affected
significantly by the time step duration when operating in isolation.  However,
even when facilities do not have individual inventory or throughput limits,
the time step can still have a significant effect. In recycle loops there is a
constraint on how fast material is introduced through the loop (i.e. the
discharge rate of spent fuel from reactors).  The \emph{inventory drawdown
effect} can impact the aggregate throughput of the recycling loop by affecting
minimum bounds on idling material quantities.

@@

TODO: thank ross maybe for vision-sourced inspiration about modeling effects
TODO: thank neup and add neup logo
